Well-quasi-orderings on word languages

### 2024-08-20 src/infixes.tex
better figures

@@

\begin{figure}
    \centering
    \includestandalone[width=\linewidth]{fig/infix-encoding-standalone}
    \caption{Representation of the \kl{subword relation} for $\set{a,b}^*$
        inside the \kl{infix relation} for $\set{a,b,c}^*$
        using the encoding of \cref{infix-embedding:thm}, restricted to words
        of length at most $3$.}
    \label{infix-embedding:fig}
\end{figure}

>>>>

\marginpar{TODO: change the encoding to take the maximal elements of the
downwards closure.}

@@

\begin{figure}
    \centering
    \includestandalone[width=\linewidth]{fig/infix-encoding-standalone}
    \caption{Representation of the \kl{subword relation} for $\set{a,b}^*$
        inside the \kl{infix relation} for $\set{a,b,c}^*$
        using the encoding of \cref{infix-embedding:thm}, restricted to words
        of length at most $3$. To obtain smaller words,
        we replaced $D_i$ by $\max D_i$ in this construction.
    }
    \label{infix-embedding:fig}
\end{figure}

The encoding using three distinct letters is clearer to use and to
illustrate, but it is not surprising that one can encode a three
letter alphabet into a two letter one, immediately
leading to the following \cref{infix-embedding-binary:cor}.

\begin{corollary}
    \label{infix-embedding-binary:cor}
    Let $(X, \preceq)$ be a \kl{partially ordered} set,
    and $\Sigma \defined \set{a,b}$.
    Then the following are equivalent:
    \begin{enumerate}
        \item \label{infix-embedding-embeds:item} 
            $X$ \kl{embeds into} $(\Sigma^*, \infleq)$,
        \item \label{infix-embedding-count:item}
            $X$ is countable, and for every $x \in X$,
            its \kl{downwards closure}
            $\dwset[\preceq]{x}$ is finite.
    \end{enumerate}
\end{corollary}
\begin{proof}
    Let us construct an \kl{order embedding} from 
    $(\set{a,b,c}^*, \infleq)$ to $(\set{0,1}, \infleq)$.
    To that end, consider
    the morphism $\mu$ that maps $a$ to $101$, $b$ to $1001$
    and $c$ to $10001$.
    Assume that $u \infleq v$ in $\set{a,b,c}^*$,
    then $\mu(u) \infleq \mu(v)$ because $\mu$ is a morphism.
    Conversely, assume that $\mu(u) \infleq \mu(v)$.
    That, is, there exists an \kl{infix} $w$ of $\mu(v)$
    such that $\mu(u) = w$.
    Because $\mu(u)$ starts with $10$ and ends with $01$, so does
    $w$. In particular, the word $w$ is compatible with $\mu$
    in the sense that $w = \mu(s)$ for some $s \infleq v$.
    Because the map $\mu$ is injective,
    we conclude that $\mu(s) = \mu(u)$ implies $s = u$
    and $u \infleq v$ as expected.
\end{proof}

### 2024-08-20 src/prefixes.tex
better figures

\begin{figure}
    \centering
    \includestandalone{src/antichain-branch-standalone}
    \caption{An \kl{antichain branch} for the language $a^* b$,
        represented in the \kl{tree of prefixes} over the alphabet $\set{a,b}$.
        The branch is represented with dashed lines in turquoise, and the
        \kl{antichain} is represented in dotted lines in blood-red.
    }
    \label{antichain-branch:fig}
\end{figure}

@@

\begin{figure}
    \centering
    TODO.
    \caption{Illustrating the construction of 
        \cref{prefixes:thm} consisting in taking the words
        that lead to prefix-incomparable elements in $S$,
        and then the upwards closure of the maximal such elements.
    }
    \label{prefixes-theorem:fig}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includestandalone{fig/antichain-branch-standalone}
    \caption{An \kl{antichain branch} for the language $a^* b$,
        represented in the \kl{tree of prefixes} over the alphabet $\set{a,b}$.
        The branch is represented with dashed lines in turquoise, and the
        \kl{antichain} is represented in dotted lines in blood-red.
    }
    \label{antichain-branch:fig}
\end{figure}

@@

\begin{figure}
    \centering
    \includestandalone[width=\linewidth]{fig/prefix-core-and-branches-standalone}
    \caption{Illustrating the construction of 
        \cref{prefixes:thm}. We represent the Hasse Diagram of a
        \kl{partial order}, with elements in $S$ being bigger and 
        in desert sand, elements of $S_{\max}$ being in
        blood-red, and \kl{chains} of elements in sky blue.
        The upwards closure of an element in $S_{\max}$ 
        is depicted in pale green, and cannot intersect two distinct
        branches, as it does not contain two incomparable elements.
    }
    \label{prefixes-theorem:fig}
\end{figure}
